### 2016-09-01 latex/paper.tex
Complete FEA table

\newpage
\section*{LIST OF TERMS}
A partial list of symbols is given below. Other symbols are defined in-place on not re-used.

\begin{tabular}{c|p{12cm}}
\hline
\textit{\textbf{Term}} & \textit{\textbf{Definition}} \\
\hline
$n_s$		& Number of spokes\\
$E_s, A_s$	& Spoke Young's modulus and cross-sectional area\\
$l$			& Spoke length\\
$\alpha$	& Out-of-plane spoke angle--wall angle of a hypothetical ``cone'' of spokes\\
$\beta$		& In-plane spoke angle--measured between the in-plane projection of the spoke and
			  a radius of the wheel\\
$\n$		& Unit vector aligned with the spoke axis\\
$\nn,\nnn$	& Two unit vectors perpendicular to the spoke axis\\
$\bm{f}$	& Force exerted by a spoke on the rim\\
$\bar{\bm{f}}$& Distributed force (per-unit-length) exerted by the spokes on the rim\\
$f_1, f_2,f_3$ & Vector components of $\bm{f}$\\
$\bm{k}_f$	& Stiffness matrix for a single spoke\\
$\bar{\bm{k}}$ & Equivalent stiffness per-unit-length of the spoke system. $\bar{\bm{k}} = \bar{\bm{k}}^{el} + \bar{\bm{k}}^{tens}$\\
$\bar{\bm{k}}^{el},\bar{\bm{k}}^{tens}$ & Part of $\bar{\bm{k}}$ proportional to $E_sA_s$ and $T$, respectively\\
$\bar{k}_{ij}$ & Matrix components of $\bar{\bm{k}}$\\
$\e,\ee,\eee$ & Coordinate axes defined at the rim shear center\\
$s$			& Arc-length coordinate along the rim\\
$\kappa_1,\kappa_2,\kappa_3$ & Spatial curvature of the rim\\
$\bm{u}$	& Displacement of the rim shear center\\
$u,v,w$		& Vector components of $\bm{u}$ in the \e{}, \ee{}, \eee{} directions.\\
$\phi$		& Rotation of the rim cross-section about the $\hat{\bm{e}}_3$ axis.\\
$\delta u, \delta \phi$ & Virtual displacement and rotation\\
$\delta u_n, \delta\phi_n$ & Buckling mode coefficients\\
$n$			& Buckling mode number\\
$U_{rim}$	& Strain energy in the rim due to buckling\\
$V_{rim}$	& Virtual work of internal forces in the rim\\
$U_{spokes}$& Strain energy in the spokes due to buckling\\
$T$			& Tension in a spoke\\
$T_{cn}$	& Critical spoke tension for the $n$th mode\\
$T_c$		& Critical buckling tension (minimum of $T_{cn}$ over all modes)\\
$T_e$		& ``Euler'' tension--tension which would produce an axial force in the rim
			  equal to the buckling load for a straight beam-column of length $2\pi R$\\
$R$			& Rim radius measured from the rim shear center\\
$E, G$		& Rim Young's modulus and shear modulus\\
$I_{11}$	& Second moment of area of the rim in the lateral direction\\
$J$			& Rim torsion constant\\
$I_w$		& Rim warping constant\\
$\widetilde{GJ}$ & Effective torsional rigidity including both Saint-Venant torsion and warping\\
$\tilde{\mu}$ & Ratio of effective torsional rigidity to bending rigidity: $\widetilde{GJ}/EI_{11}$\\
$\lambda$	& Ratio of spoke system lateral stiffness to rim bending stiffness OR ratio
			  of rim radius to the characteristic length of a beam on an elastic foundation.\\
\hline
\end{tabular}

>>>>

\newpage
\section*{LIST OF TERMS}

\begin{table}[ht!]
\caption{A partial list of symbols is given below. Other symbols are defined in-place or not re-used.}
\begin{tabular}{c|p{12cm}}
\hline
\textit{\textbf{Term}} & \textit{\textbf{Definition}} \\
\hline
$n_s$		& Number of spokes\\
$E_s, A_s$	& Spoke Young's modulus and cross-sectional area\\
$l$			& Spoke length\\
$\alpha$	& Out-of-plane spoke angle--wall angle of a hypothetical ``cone'' of spokes\\
$\beta$		& In-plane spoke angle--measured between the in-plane projection of the spoke and
			  a radius of the wheel\\
$\n$		& Unit vector aligned with the spoke axis\\
$\nn,\nnn$	& Two unit vectors perpendicular to the spoke axis\\
$\bm{f}$	& Force exerted by a spoke on the rim\\
$\bar{\bm{f}}$& Distributed force (per-unit-length) exerted by the spokes on the rim\\
$f_1, f_2,f_3$ & Vector components of $\bm{f}$\\
$\bm{k}_f$	& Stiffness matrix for a single spoke\\
$\bar{\bm{k}}$ & Equivalent stiffness per-unit-length of the spoke system. $\bar{\bm{k}} = \bar{\bm{k}}^{el} + \bar{\bm{k}}^{tens}$\\
$\bar{\bm{k}}^{el},\bar{\bm{k}}^{tens}$ & Part of $\bar{\bm{k}}$ proportional to $E_sA_s$ and $T$, respectively\\
$\bar{k}_{ij}$ & Matrix components of $\bar{\bm{k}}$\\
$\e,\ee,\eee$ & Coordinate axes defined at the rim shear center\\
$s$			& Arc-length coordinate along the rim\\
$\kappa_1,\kappa_2,\kappa_3$ & Spatial curvature of the rim\\
$\bm{u}$	& Displacement of the rim shear center\\
$u,v,w$		& Vector components of $\bm{u}$ in the \e{}, \ee{}, \eee{} directions.\\
$\phi$		& Rotation of the rim cross-section about the $\hat{\bm{e}}_3$ axis.\\
$\delta u, \delta \phi$ & Virtual displacement and rotation\\
$\delta u_n, \delta\phi_n$ & Buckling mode coefficients\\
$n$			& Buckling mode number\\
$U_{rim}$	& Strain energy in the rim due to buckling\\
$V_{rim}$	& Virtual work of internal forces in the rim\\
$U_{spokes}$& Strain energy in the spokes due to buckling\\
$T$			& Tension in a spoke\\
$T_{cn}$	& Critical spoke tension for the $n$th mode\\
$T_c$		& Critical buckling tension (minimum of $T_{cn}$ over all modes)\\
$T_e$		& ``Euler'' tension--tension which would produce an axial force in the rim
			  equal to the buckling load for a straight beam-column of length $2\pi R$\\
$R$			& Rim radius measured from the rim shear center\\
$E, G$		& Rim Young's modulus and shear modulus\\
$I_{11}$	& Second moment of area of the rim in the lateral direction\\
$J$			& Rim torsion constant\\
$I_w$		& Rim warping constant\\
$\widetilde{GJ}$ & Effective torsional rigidity including both Saint-Venant torsion and warping\\
$\tilde{\mu}$ & Ratio of effective torsional rigidity to bending rigidity: $\widetilde{GJ}/EI_{11}$\\
$\lambda$	& Ratio of spoke system lateral stiffness to rim bending stiffness OR ratio
			  of rim radius to the characteristic length of a beam on an elastic foundation.\\
\hline
\end{tabular}
\end{table}

\newpage
\section*{FINITE-ELEMENT RESULTS}
For all the following wheels: $R=0.3$ m, $EI_{11}=EI_{22}=69.0$ N-m$^2$, $GJ=26.0$ N-m$^2$, $I_w=0$, $E_s=210$ GPa. The cross-sectional area of the rim is 100 mm$^2$. All length measurements in the following table are given in mm. $T_c$ is reported in Newtons. Hub flange width is the distance from the drive-side flange to the left-side flange. Hub flange diameter is the diameter of the circle that passes through the centers of the spoke eyelets.

\begin{table}[ht!]
\caption{Parameters for FEA simulations shown in Fig \ref{fig:Tc_nondim} (b).}
\begin{tabular}{c|c|c|c|c|c}
\hline
$n_s$	& Spoke diameter	& Hub flange width	& Hub flange diameter	& $T_c$ ABAQUS	& $T_c$ theory\\
\hline
36		& 0.693				& 50				& 40					& 477			& 475\\
36		& 0.981				& 50				& 40					& 668			& 704\\
\hline
48		& 1.040				& 50				& 40					& 694			& 698\\
48		& 1.201				& 50				& 40					& 862			& 870\\
48		& 1.343				& 50				& 40					& 956			& 942\\
48		& 1.471				& 50				& 40					& 1021			& 1005\\
48		& 1.900				& 50				& 40					& 1270			& 1259\\
48		& 1.943				& 60				& 40					& 1563			& 1573\\
\hline
64		& 1.671				& 60				& 40					& 1450			& 1418\\
\end{tabular}
\end{table}

For all the following wheels: $n_s=36$, $R=0.3$ m, hub flange width = $50$ mm, hub flange diameter = $40$ mm, spoke diameter = $0.981$ mm, $EI_{11}=EI_{22}=69.0$ N-m$^2$, $I_w=0$, $E_s=210$ GPa. $GJ$ varies with $\mu$ given in the table below. The cross-sectional area of the rim is 100 mm$^2$. $T_c$ is reported in Newtons.

\begin{table}[ht!]
\centering
\caption{Parameters for FEA simulations shown in Fig \ref{fig:Tc_nondim} (c).}
\begin{tabular}{c|c|c}
\hline
$\mu$	& $T_c$ ABAQUS & $T_c$ theory\\
\hline
0.001	& 154	& 121 \\
0.00215	& 191	& 157 \\
0.00464	& 220	& 212 \\
0.01	& 264	& 258 \\
0.0215	& 359	& 344 \\
0.0464	& 501	& 487 \\
0.1		& 556	& 574 \\
0.215	& 624	& 646 \\
0.464	& 701	& 723 \\
1		& 759	& 785 \\
\end{tabular}
\end{table}
